Practicing with the data

### 2017-07-04 new_variables.Rmd
practicing with dplyr

---
title: "New Variables"
author: "Lisa Oshita"
date: "June 29, 2017"
output:
  pdf_document: default
  html_document: default
---

### Creating time to event variable
observation 15 has a negative value?
```{r}

out$time_until_answer <- out$first_answer_date - out$post_date

@@

>>>>

---
title: "Practicing with the data"
author: "Lisa Oshita"
date: "June 29, 2017"
output:
  pdf_document: default
  html_document: default
---

### Creating time to event variable
observation 15 has a negative value?
```{r}
out$time_until_answer <- out$first_answer_date - out$post_date

@@

### Practicing with dplyr
```{r}
library(dplyr)

#using only observations in English
out1 <- out %>% 
          tbl_df() %>% 
          filter(langid == "en")

#view average time until answered grouped by each category 
out1 %>%
  group_by(category) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(avg_time)

#view average time until answered grouped by whether or not question contains "?"
#seems like for a lot of categories, questions with question marks get answered faster
out1$contain_questionmark <- str_detect(out1$title, pattern = QUESTION)
out1 %>%
  group_by(category, contain_questionmark) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(category, avg_time)

#looking at average time until answered for intervals of title length
library(stringr)
title_length <- str_length(out1$title)
out1$title_length_intervals <- cut(length, breaks = 8)
#don't really see anything interesting here 
out1 %>%
  group_by(title_length_intervals) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n())
